Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
Outline of the clustering method.

\subsection*{Cluster analysis}

>>>>

\subsection*{Cluster analysis}
% 1. Clustering focusing on 11 water accessibility variables
% 2. Different clustering algorithm for initial analysis
% 3. Determination and analysis of best cut and hierarchical clustering method
% 4. Election of the best clustering
% 5. Analysis of Ward.d2 & 4 cut tree analysis

We elected 11 variables which describes water accessibility of 78 countries around the world \citep{price2019difference}. Next, we decided to implement clustering which is an unsupervised machine learning method to identify and group water accessibility variables in large data set to understand and make inference about particular water accessibility variables. Clustering ultimately can continue to assist on discovering the water accessibility predictor variables. 
First, we

%Kwale County is located on the south coast of Kenya, between the city of Mombasa to the north, and Tanzania to the south. In 2013, Kwale had a population of approximately 730,000 people, four‐fifths of whom lived in rural areas [Commission on Revenue Allocation, 2013]. Based on a poverty gap index measure, the region is one of the most impoverished in Kenya, ranked 41st out of 47 counties [Commission on Revenue Allocation, 2013]. According to the census in 2009, protected wells and boreholes were the main sources of water for 21.9% of the county's households [Kenya National Bureau of Statistics, 2012].
